Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-07-22 ms.tex
Minor changes
Finished the Fermi-LAT result table; minor tweaks

\usepackage{lscape}

@@

\section{Dark Matter}

@@

\begin{deluxetable}{lcc}
\tablecolumns{3}
\tablewidth{0pc}
\tablecaption{Regions of interest in the Coma cluster field of view.}
\tablehead{
\colhead{Source} &
\colhead{RA} &
\colhead{Dec}}
\startdata
Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0}\\
NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03}\\
NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37}\\
NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59}\\
\enddata
\tablecomments{The cluster core is considered both as a point source and a modestly extended source. Three central galaxies are also considered in point-source searches. The choice is based on evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the location of these galaxies.}
\label{table:roi}
\end{deluxetable}

\begin{landscape}
\begin{deluxetable}{lccccccccc}
\tablecolumns{10}
\tablewidth{0pc}
\tablecaption{Flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings.}
\tablehead{
\colhead{Source} & \colhead{RoI\tablenotemark{a} [deg]} & \colhead{$N_{S}$} & \colhead{S\tablenotemark{b} [$\sigma$]} &
\multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} \\
\colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=2.1$} &
\multicolumn{2}{c}{$\alpha=2.3$} &
\multicolumn{2}{c}{$\alpha=2.5$}}
\startdata
Core & 0 & 17 & 0.84 & 2.59 & (0.78\%) & 2.78 & (0.83\%) & 2.97 & (0.89\%) \\
& 0.2 & -41 & -1.0 & 1.96 & (0.59\%)  & 2.09 & (0.63\%) & 2.21 & (0.66\%) \\
& 0.4 & -26 & -0.30 & 4.44 & (1.3\%)  & 4.74 & (1.4\%) & 5.02 & (1.5\%)\\
NGC 4889 & 0 & 3 & 0.14 & - & - & 1.85 & (0.55\%)  & - & - \\
NGC 4874 & 0 & -14 & -0.71 & - & - &  1.51 & (0.45\%)  & - & - \\
NGC 4921 & 0 & -4 & -0.23 & - & - &  2.41 & (0.72\%)  & - & -
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
\tablenotetext{b}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
\tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
\label{table:results}
\end{deluxetable}
\end{landscape}

\begin{landscape}
\begin{deluxetable}{cccccccccccc}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions.} 
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
0 & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
\tablenotetext{c}{Integrated gamma-ray flux $F(>E=220~\mathrm{GeV}$) in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$ in the simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
\tablenotetext{c}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$ that was assumed to be constant throught the cluster; calculated according to \citet{article:PfrommerEnsslin:2004b}.}
\tablenotetext{e}{Minimum gamma-ray flux $F_{\rmn{min}}(>E=220~\mathrm{GeV}$) in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ for energies above $E=220~\rmn{GeV}$ of the hadronic model described in the text.}
\label{table:constraints}
\end{deluxetable}
\end{landscape}

\begin{deluxetable}{cccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster.}
\tablehead{
\colhead{$\alpha_{B}$} &
\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}}
\startdata
0.3 & 0.61 & 0.51 & 0.43 \\
0.5 & 0.82 & 0.68 & 0.58 \\
0.7 & 1.19 & 0.98 & 0.83 
\enddata
\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
\label{table:Bmin}
\end{deluxetable}

\begin{deluxetable}{lcccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core.}
\tablehead{
\colhead{Spatial model} & \multicolumn{6}{c}{Flux U.L.}
}
\startdata
Point source & 1.73 & 1.81 & 0.487 & 0.526 & 0.627 & 0.635
\enddata
\label{table:fermi}
\end{deluxetable}

>>>>

@@

\section{Emission from Dark Matter Annihilations}

@@

\begin{deluxetable}{lcc}
\tablecolumns{3}
\tablewidth{0pc}
\tablecaption{Regions of interest in the Coma cluster field of view.}
\tablehead{
\colhead{Source} &
\colhead{RA} &
\colhead{Dec}
}
\startdata
Core & \RA{12}{59}{48.7} & \Dec{+27}{58}{50.0}\\
NGC 4889 & \RA{13}{00}{08.13} & \Dec{+27}{58}{37.03}\\
NGC 4874 & \RA{12}{59}{35.71} & \Dec{+27}{57}{33.37}\\
NGC 4921 & \RA{13}{01}{26.12} & \Dec{+27}{53}{09.59}\\
\enddata
\tablecomments{The cluster core is considered both as a point source and a modestly extended source. Three central galaxies are also considered in point-source searches. The choice is based on evidence of an excess of non-thermal X-ray emission \citep{article:Neumann_etal:2003} at the location of these galaxies.}
\label{table:roi}
\end{deluxetable}

\begin{deluxetable}{lccccccccc}
\tablecolumns{10}
\tablewidth{0pc}
\tablecaption{Flux upper limits for different regions of interest in the Coma cluster of galaxies and surroundings.}
\rotate
\tablehead{
\colhead{Source} & \colhead{RoI\tablenotemark{a} [deg]} & \colhead{$N_{S}$} & \colhead{S\tablenotemark{b} [$\sigma$]} &
\multicolumn{6}{c}{Flux U.L.\tablenotemark{c}} \\
\colhead{} & \colhead{} & \colhead{} & \colhead{} & \multicolumn{2}{c}{$\alpha=2.1$} &
\multicolumn{2}{c}{$\alpha=2.3$} &
\multicolumn{2}{c}{$\alpha=2.5$}
}
\startdata
Core & 0 & 17 & 0.84 & 2.59 & (0.78\%) & 2.78 & (0.83\%) & 2.97 & (0.89\%) \\
& 0.2 & -41 & -1.0 & 1.96 & (0.59\%)  & 2.09 & (0.63\%) & 2.21 & (0.66\%) \\
& 0.4 & -26 & -0.30 & 4.44 & (1.3\%)  & 4.74 & (1.4\%) & 5.02 & (1.5\%)\\
NGC 4889 & 0 & 3 & 0.14 & - & - & 1.85 & (0.55\%)  & - & - \\
NGC 4874 & 0 & -14 & -0.71 & - & - &  1.51 & (0.45\%)  & - & - \\
NGC 4921 & 0 & -4 & -0.23 & - & - &  2.41 & (0.72\%)  & - & -
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
\tablenotetext{b}{Statistical significance calculated according to \citet{article:LiMa:1983}.}
\tablenotetext{c}{99\% confidence level upper limit in units of $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ calculated according to \citet{article:Rolke_etal:2005} above an energy threshold of 220 GeV, with corresponding fluxes in percent of the steady Crab Nebula flux in parenthesis.}
\label{table:results}
\end{deluxetable}

\begin{deluxetable}{cccccccccccc}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions.} 
\rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
0 & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
\tablenotetext{c}{Integrated gamma-ray flux above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$; simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
\tablenotetext{e}{Minimum gamma-ray flux in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$, for energies $E>220~\rmn{GeV}$ in the hadronic model described in the text.}
\label{table:constraints}
\end{deluxetable}

\begin{deluxetable}{cccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster.}
\tablehead{
\colhead{$\alpha_{B}$} &
\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
0.3 & 0.61 & 0.51 & 0.43 \\
0.5 & 0.82 & 0.68 & 0.58 \\
0.7 & 1.19 & 0.98 & 0.83 
\enddata
\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
\label{table:Bmin}
\end{deluxetable}

\begin{deluxetable}{lcccccc}
\tablecolumns{7}
\tablewidth{0pc}
\tablecaption{\emph{Fermi}-LAT upper limits for the Coma cluster core.}
\tablehead{
\colhead{Spatial model} & \multicolumn{3}{c}{S[$\sigma$]} & \multicolumn{3}{c}{Flux U.L.} \\
\colhead{} & \colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} & 
\colhead{1-3 GeV} & \colhead{3-10 GeV} & \colhead{10-30 GeV} \\
\hline
\multicolumn{7}{c}{Spectral index $\alpha=2.1$ (fixed)}
}
\startdata
Point source & 0.30 & 0 & 1.3 & 1.73 & 4.87 & 0.627 \\
Disk, $r=0.2^{\circ}$ & 0.65 & 0.22 & 2.0 & 2.03 & 0.691 & 0.783 \\
Disk, $r=0.4^{\circ}$ & 0.77 & 0.18 & 2.3 & 2.39 & 0.757 & 0.847 \\
\cutinhead{Spectral index $\alpha=2.5$ (fixed)}
Point source & 0.33 & 0 & 1.42 & 1.81 & 0.526 & 0.635 \\
Disk, $r=0.2^{\circ}$ & 0.66 & 0.35 & 2.1 & 2.12 & 0.748 & 0.785 \\
Disk, $r=0.4^{\circ}$ & 0.80 & 0.36 & 2.4 & 2.50 & 0.833 & 0.849 \\
\enddata
\label{table:fermi}
\end{deluxetable}
